Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
finish refactoring abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The emerging field of computational ecoacoustics aims at retrieving high-level information from the acoustic scenes recorded by some network of sensors.
In this context, a central task is to cluster acoustic scenes by similarity.
A convenient method considers bag-of-frames models and other representations based on summary statistics.
While these successfully characterize static scenes with little variability in sound content, they are unable to accurately differentiate scenes characterized by a few distinct sound events superimposed over a static background.
To address this problem, we propose a two-scale representation, which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure.
To motivate this, we validate the use of scattering transforms for supervised acoustic scene classification (ASC), illustrating its state-of-the-art performance compared to traditional features, such as mel-frequency cepstral coefficients (MFCCs).
Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) task, where we again significantly outperform more traditional approaches based on summary statistics of MFCCs.

\end{abstract}

@@

An important problem in this field is the characterization of auditory scenes for the purposes of similarity estimation. One application of this is acoustic scene similarity retrieval (ASSR), where the scenes judged ``most similar'' to a given query scene are extracted from some larger dataset. This requires the auditory scenes to be represented in some way that captures their distinctive qualities. Often, this has been achieved by bag-of-frames approaches \cite{aucouturier2007bag}, which attempt to describe the auditory scene recording using summary statistics. Unfortunately, since this only captures the average structure of the scene, the approach often fails when presented scenes which are dynamic and contain episodic, distinct sound events that discriminate the scene from others. Indeed, experiments in cognitive psychology \cite{dubois2006cognitive} and cognitive neurosciences \cite{nelken2004processing} suggest that this matches more closely the way that humans perceive acoustic scenes.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The emerging field of computational ecoacoustics aims at retrieving high-level information from the acoustic scenes recorded by some network of sensors.
In this paper, we address the problem of acoustic scene classification (ASC) according to the taxonomy of the DCASE 2013 challenge, both in supervised and unsupervised settings.
Traditional approaches compute a "bag-of-frames", i.e. the summary statistics of short-term audio descriptors, such as mel-frequency cepstral coefficients (MFCCs).
Although they successfully characterize static scenes with little variability in auditory content, they are unable to accurately discriminate scenes with few salient events superimposed over a textured background.
To overcome this issue, we propose a two-scale representation which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure.
We validate the use of the scattering transform for supervised acoustic scene classification by reporting a better accuracy than MFCCs when using a support vector machine (SVM) classifier.
Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) unsupervised task, where we significantly outperform more traditional approaches based on summary statistics of MFCCs.
\end{abstract}

@@

An important problem in this field is the characterization of auditory scenes for the purposes of similarity estimation. One application of this is acoustic scene similarity retrieval (ASSR), where the scenes judged ``most similar'' to a given query scene are extracted from some larger dataset. This requires the auditory scenes to be represented in some way that captures their distinctive qualities. Often, this has been achieved by bag-of-frames approaches \cite{aucouturier2007bag}, which attempts to describe the auditory scene recording using summary statistics. Unfortunately, since this only captures the average structure of the scene, the approach often fails when presented scenes which are dynamic and contain episodic, distinct sound events that discriminate the scene from others. Indeed, experiments in cognitive psychology \cite{dubois2006cognitive} and cognitive neurosciences \cite{nelken2004processing} suggest that this matches more closely the way that humans perceive acoustic scenes.
